### 2025-01-27 week1/project1.tex
init

\documentclass[12pt]{article}

%
%Margin - 1 inch on all sides
%
\usepackage[letterpaper]{geometry}
\usepackage{times}
\geometry{top=1.0in, bottom=1.0in, left=1.0in, right=1.0in}

%
%Doublespacing
%
\usepackage{setspace}
\doublespacing

%
%Rotating tables (e.g. sideways when too long)
%
\usepackage{rotating}

%
%Fancy-header package to modify header/page numbering (insert last name)
%
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\rhead{Jammishetti \thepage}
\lfoot{}
\cfoot{}
\rfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
%To make sure we actually have header 0.5in away from top edge
%12pt is one-sixth of an inch. Subtract this from 0.5in to get headsep value
\setlength\headsep{0.333in}

%
%Works cited environment
%(to start, use \begin{workscited...}, each entry preceded by \bibent)
% - from Ryan Alcock's MLA style file
%
\newcommand{\bibent}{\noindent \hangindent 40pt}
\newenvironment{workscited}{\newpage \begin{center} Works Cited \end{center}}{\newpage }

%
%Begin document
%
\begin{document}
\begin{flushleft}

	%%%%First page name, class, etc
	Surendra Jammishetti\\
	Professor Kirsh\\
	Writing 2\\
	January 07 2025\\

	%%%%Title
	\begin{center}
		Project 1
	\end{center}

	%%%%Changes paragraph indentation to 0.5in
	\setlength{\parindent}{0.5in}
	%%%%Begin body of paper here

	I'd say I'm much more of a reader than a writer, and frankly, I'm disappointed about that.
	Maybe that's because I'm burnt out after college apps / AP tests where I had to think
	about what others wanted to hear and follow a semi-strict format, instead of writing what
	I wanted to write. The most natural style of writing is my inner monologue, especially when
	I'm writing comments in my code. There'll be questions and short snips, and I like
	doing that because it feels more personal. It leaves a part of me inside of it
	rather than it just being some obscure computer program. Other than that, I think that
	my writing doesn't have a voice.

	While I'd say I was pretty good at "academic" writing back in high school,
	it never really felt like I was just writing. I desire the feeling of writing
	down my thoughts, where it feels like the reader is going to get to know me as
	a person. That's the kind of writing I enjoy. The kind of writing that doesn't follow
	conventional rules, and is rather more personable. I want my writing to be a reflection
	of me, like a hologram or a phone call.

	Now the majority of my writing consists of text messages, and coding, not sure if that
	counts or not. According to PACT, I "am" writing my code with a purpose, my audience being
	the users, within the context of a project / my interests, and yeah code is textual so I'm hoping that
	makes me a writer. Now that I think about it, writing anything does have a certain
	depth to it, which is why I'm partially disappointed in myself for not writing more. It
	feels like I'm missing out on an integral part of the human experience.

	I value writing skills in today's world, mostly because of what Genai is
	allowing us students to do. I dislike how it's being used to "complete"
	things. It has always struck me the wrong way, because I take pride in the work
	that I do, so using something else and calling it mine just feels paradoxical.
	Additionally, it all sounds the same. There's no personality. There was this
	critique I saw, where Apple is using AI to summarize text messages, and they are
	also using AI to write text messages, you can give it a summary of what you want
	it to say and it generate it. What does this mean? The future is going to
	consist of us writing bullet points and reading bullet points and there's
	going to be bland and verbose text as the middle man. It's disturbing. I want
	to take pride in the things I write, being able to say that these
	words came from my head, unassisted, these words are a snapshot of myself in time.

	I tried to start a blog a couple of months back, it's on my website (www.suri.codes if you're interested in checking it out).
	I was excited to write about some of the things I was working on and got one
	blog post successfully made but that was the end of that. As school, research, and work
	just started piling up, I lost interest, and motivation, to keep working on the blog.
	I'm hoping that this class helps me flex my muscles enough, and reignites the spark so
	I can at least get a couple more posts up on my blog.

	\newpage

	%%%%Title
	% \begin{center}
	% 	Notes
	% \end{center}

	% \setlength{\parindent}{0.5in}

	% 1. Danhof includes “Delaware, Maryland, all states north of the Potomac and Ohio rivers, Missouri, and states to its north” when referring to the northern states (11).

	% 2. For the purposes of this paper,“science” is defined as it was in nineteenthcentury agriculture: conducting experiments and engaging in research.

	% 3. Please note that any direct quotes from the nineteenth century texts are writtenin their original form, which may contain grammar mistakes according to twenty-first century grammar rules.

	%%%%Works cited
	% \begin{workscited}

	% 	\bibent
	% 	Allen, R.L. \textit{The American Farm Book; or Compend of Ameri can Agriculture; Being a Practical Treatise on Soils, Manures, Draining, Irrigation, Grasses, Grain, Roots, Fruits, Cotton, Tobacco, Sugar Cane, Rice, and Every Staple Product of the United States with the Best Methods of Planting, Cultivating, and Prep aration for Market.} New York: Saxton, 1849. Print.

	% 	\bibent
	% 	Baker, Gladys L., Wayne D. Rasmussen, Vivian Wiser, and Jane M. Porter. \textit{Century of Service: The First 100 Years of the United States Department of Agriculture.}[Federal Government], 1996. Print.

	% 	\bibent
	% 	Danhof, Clarence H. \textit{Change in Agriculture: The Northern United States, 1820-1870.} Cambridge: Harvard UP, 1969. Print.

	% \end{workscited}

\end{flushleft}
\end{document}
\}

### 2025-01-27 week3/main.tex
init

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Welcome to Overleaf --- just edit your LaTeX on the left,
% and we'll compile it for you on the right. If you open the
% 'Share' menu, you can invite other users to edit at the same
% time. See www.overleaf.com/learn for more info. Enjoy!
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}
\usepackage[
backend=biber,
style=ieee,
]{biblatex}
\title{Annotated Bibliography}
\addbibresource{sample.bib} %Imports bibliography file

\begin{document}

\maketitle

All citations are in IEEE Style, as I want some foray into writing academic papers in
the computer science field.

% A brief annotation (150-200 words) which does all four of the following:
% Identifies the purpose/s of the source (What change do you think the author hoped would happen when people read this source?) 
% Explains who you think the intended audience of the source is, and why you think this
% Explains some key strengths of the source and how it can be useful as you investigate your topic
% Explains possible limitations or weaknesses you see in the source
% (eg. credibility, scope of information, author bias, etc.) Keep in mind
% that you might have to do a little additional research to get some other
% perspectives on your source to evaluate its reliability (eg. book reviews,
% author bios, original publication dates etc.)

\section{Book}

Citation: \cite{stokes2021}
Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/15r5l0d/alma991025892758804876

\section{Newspaper}

Citation: \cite{thomas2024}
Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_proquest_newspapers_2937453324

\section{Paper}

Citation: \cite{ma2024}
Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_ieee_primary_10440501

\section{Video}

Citation: \cite{bloomberglaw2023}
Link: https://www.youtube.com/watch?v=bRqwTP2eKJY

\medskip

\printbibliography
\end{document}

### 2025-01-28 week3/main.tex
tearsitn

@@
 \title{Annotated Bibliography}
+
 \addbibresource{sample.bib} %Imports bibliography file
@@
 Citation: \cite{stokes2021}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/15r5l0d/alma991025892758804876
+Link: \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/15r5l0d/alma991025892758804876}
+
+The purpose of the book is to educate those looking into copyright law
+for art and the various rules that apply to different types of art, even those of non-conventional medium.
+As for the intention of the author writing this book, I believe he desired to
+provide a compilation of guidelines regarding various different areas that copyright touches on
+regarding art and derivative works. I'm rationalizing his purpose as the main consumers
+of his book are those who work in art law, ip law, law students, art house managers,
+and others in the field, who regard his book as a critical source of truth regarding
+common copyright misunderstandings and education. I intend to use this source
+to understand the basics of copyright law and gain some insight on how copyright law
+has applied to derivative works in the past. In esscence, I plan to use this source to develop
+the foundation of copyright that my essay will build upon. Some weaknesses with this source
+is that it was published in 2001, almost 24 years ago, so I doubt that it'll include anything of
+value regarding AI.
 
@@
 Citation: \cite{thomas2024}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_proquest_newspapers_2937453324
+Link: \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CD_SCR_INST/ojisf2/cdi_proquest_newspapers_2937453324}
 
@@
 Citation: \cite{ma2024}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_ieee_primary_10440501
+Link: \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CD_SCR_INST/ojisf2/cdi_ieee_primary_10440501}
 

### 2025-02-14 paper/main.tex
papertime

%% Lab Report for EEET2493_labreport_template.tex
%% V1.0
%% 2019/01/16
%% This is the template for a Lab report following an IEEE paper. Modified by Francisco Tovar after Michael Sheel original document.

%% This is a skeleton file demonstrating the use of IEEEtran.cls
%% (requires IEEEtran.cls version 1.8b or later) with an IEEE
%% journal paper.
%%
%% Support sites:
%% http://www.michaelshell.org/tex/ieeetran/
%% http://www.ctan.org/pkg/ieeetran
%% and
%% http://www.ieee.org/

%%*************************************************************************
%% Legal Notice:
%% This code is offered as-is without any warranty either expressed or
%% implied; without even the implied warranty of MERCHANTABILITY or
%% FITNESS FOR A PARTICULAR PURPOSE! 
%% User assumes all risk.
%% In no event shall the IEEE or any contributor to this code be liable for
%% any damages or losses, including, but not limited to, incidental,
%% consequential, or any other damages, resulting from the use or misuse
%% of any information contained here.
%%
%% All comments are the opinions of their respective authors and are not
%% necessarily endorsed by the IEEE.
%%
%% This work is distributed under the LaTeX Project Public License (LPPL)
%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
%% distributed and modified. A copy of the LPPL, version 1.3, is included
%% in the base LaTeX documentation of all distributions of LaTeX released
%% 2003/12/01 or later.
%% Retain all contribution notices and credits.
%% ** Modified files should be clearly indicated as such, including  **
%% ** renaming them and changing author support contact information. **
%%*************************************************************************

\documentclass[journal]{IEEEtran}

% *** CITATION PACKAGES ***
\usepackage[style=ieee]{biblatex} 
\bibliography{main.bib}    %your file created using JabRef

% *** MATH PACKAGES ***
\usepackage{amsmath}

% *** PDF, URL AND HYPERLINK PACKAGES ***
\usepackage{url}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}
\usepackage{graphicx}  %needed to include png, eps figures
\usepackage{float}  % used to fix location of images i.e.\begin{figure}[H]

\begin{document}

% paper title
\title{Analyzing the Effectiveness of Copyright Law on AI Output in Software
Engineering and Future Developments}

% author names 
\author{Surendra Jammishetti, sjammish@ucsc.edu}% <-this % stops a space

% The report headers
\markboth{Writing 2 Final Argumentative Essay, February 2025}%do not delete next lines
{Shell \MakeLowercase{\textit{et al.}}: Bare Demo of IEEEtran.cls for IEEE Journals}

% make the title area
\maketitle

% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\begin{abstract}
TODO: need to do this later
\end{abstract}

\begin{IEEEkeywords}
AI, Software Engineering, Copyright
\end{IEEEkeywords}

\section{Introduction}
% want to talk about the problem space
% rise of artificial intelligence
% tools like github copilot, cursor AI editor
% widespread usage by college students,
% talk about github marketing code efficiency 
% just state thesis
%
%

\IEEEPARstart{W}{rite} why is important to do this experiment, what background is needed, what technology has been used in this session, you can also talk briefly about what other technology exist but was not used here.
Then explain briefly how the experiment was conducted, what measurements were taken, what technology is used (acquisition system, sensors, software), if calculations were done, what calculations were done, what decisions were made, and what the final result was (explained in a concise way with words).
Writing “good” reports requires much thought, organization and editing but the rewards are
great. Those students who can master good technical writing skills will find greater success and
opportunity as professionals in industry.

% \\
%thesis
For those concerned with the legality of the software they produce, the usage of
AI-generated code should be avoided as their trustworthiness is dubious and
they will become succeptible to copyright law in the near future.

\section{Background}

% - Go down into the history of copyright, what its
% definition is, and how it has been interpreted in the past. Really tie
% it in for the reader so it's fully clear how my argument builds upon
% this foundational information.
%   - The book by Stokes should have a lot of relevant information that
%     I can summarize and cite in this section.

% -An aside / short paragraph about the overlap between copyright and code.
% Talk about Google vs. Oracle and how modern software practices software
% through the idea of licenses. It's really important that this point
% gets understood by the reader, so add examples / pictures from GitHub?
%   - The article by Harvard Law Review going over the Google v. Oracle
%     case should give enough information to summarize the technical details
%     for the audience so they have a basic understanding. I can cite one
%     of the most widely used licenses and show how they apply to the code
%     in repositories, i.e., the MIT license.

% - Usage of AI tools in software engineering. Background information about
% how artificial intelligence tools have broken into the industry today
% and the prevalence of their usage. I can cite the paper:
%   - "Recent research [15] has demonstrated that large PLG [Programming
%     Language Generation] models such as GPT-J [89] can accomplish
%     computer science assignments for students without triggering MOSS
%     [76], a widely used academic plagiarism detection tool." (page 2,
%     1st paragraph, academic paper)

\section{AI and Code Generation}

% - It's already hard to fit AI-generated anything into a box right now.
%     - Thomas's newspaper talks about how implementing regulation against
%     AI-made works has failed in the UK.

% - The lack of rules has allowed "rule breakage" of honest, well-intentioned
% standards already placed within the community, such as how AI companies
% are ignoring robots.txt.
%   - This paragraph is probably going to be a bit longer, or
%     I might split it up into two—one where I explain what a
%     robots.txt is, and the second going into the dishonest behavior.
%     https://mjtsai.com/blog/2024/06/24/ai-companies-ignoring-robots-txt/

% - Code is being written today that uses the output of these thinking
% machines—code that's going to be integrated into existing
% codebases. Any ruling in the future is going to impact code that was
% written today. It's a very murky area to be in as a company right now.

% - Additionally, as a company, it can be a liability for your own code
% through the usage of these tools because there is no guarantee that they
% aren't harvesting your code as they write it.
%     More of a cybersecurity angle.

% TODO: maybe change this name?
\section{Tracking}

% This part of my research paper is going to delve deep into the ideas and
% presentations made in the research paper about back-tracking the results of
% artificial intelligence to their source. Using this evidence, I plan to make
% a logical argument that in the future, with technology like this advancing,
% if we can find the source of any source code, and if it's similar enough,
% it makes a valid enough case for a copyright violation. Using this, I'll
% argue that for those who are concerned about the legality of their code,
% it's better to avoid using tools that spit out code, as the risk can be
% too high.

\section{Discussion and Summary}

% Summarize my point with an emphasis on my thesis.

\appendices
\section{Hand calculations (or name your title for appendix subtitle)}
List any extra evidence such as photos of the session, that may help you support your claims.
You can include all hand calculations, extra graphs and plots, simulation results, etc.

% use section* for acknowledgment
\section*{Acknowledgment}
The authors would like to thank...

\printbibliography

% Examples of references:  \\[0.001in]

% Example of data book:\\[0.1in]
% [2] National Operational Amplifiers Databook. Santa Clara: National Semiconductor
% Corporation, 1995 Edition, p. I-54. \\[0.1in]
% Example of textbook: \\[0.1in]
% [3]M. Young, The Technical Writer’s Handbook. Mill Valley, CA: University Science, 1989.\\[0.1in]
% Example of scientific journal paper:\\[0.1in]
% [4] J.W. Smith, L.S. Alans and D.K. Jones, “An operational amplifier approach to
% active cable modeling”, IEEE Transactions on Modeling, vol. 4, no. 2, 1996, pp.
% 128-132.\\[0.1in]
% Example of conference paper proceedings:\\[0.1in]
% [5] J.W. Smith, L.S. Alans and D.K. Jones, “Active cable models for lossy
% transmission line circuits”, in Proc. 1995 IEEE Modeling Symposium, 1996, pp.
% 1086-89.\\[0.1in]

% Example of Internet web page:\\[0.1in]
% [6] Approximate material properties in isotropic materials. Milpitas, CA: Specialty
% Engineering Associates, Inc. web site: www.ultrasonic.com, downloaded Aug. 20,
% 2001.

% List and number all bibliographical 
% references at the end of your paper in {\bf 9 or 10 point} Times, with 10-point interline spacing. When referenced within the text, enclose the citation number in square brackets, for example [1]. \\
% Use IEEE format. Cite any external work that you used (data sheets, text books, Wikipedia articles, . . . ). If you get a formula from a Wikipedia article, you must cite the article, giving the title, the URL, and the data you accessed the article as a minimum. If you copy a figure, not only must you cite the article you copied from, but you must give explicit figure credit in the caption for the figure: This image copied from . . . . If you modify a figure or base your figure on one that has been published elsewhere, you still need to give credit in the caption: This image adapted from . . . .\\[0.1in]

% that's all folks
\end{document}

### 2025-02-14 week3/main.tex
papertime

--- 2025-01-27 week3/main.tex
@@
 
-All citations are in IEEE Style, as I want some foray into writing academic papers in
-the computer science field.
+All citations are in IEEE Style, as I want some foray into writing academic
+papers in the computer science field.
 
-% A brief annotation (150-200 words) which does all four of the following:
-% Identifies the purpose/s of the source (What change do you think the author hoped would happen when people read this source?) 
-% Explains who you think the intended audience of the source is, and why you think this
-% Explains some key strengths of the source and how it can be useful as you investigate your topic
-% Explains possible limitations or weaknesses you see in the source
-% (eg. credibility, scope of information, author bias, etc.) Keep in mind
-% that you might have to do a little additional research to get some other
-% perspectives on your source to evaluate its reliability (eg. book reviews,
-% author bios, original publication dates etc.)
+% % A brief annotation (150-200 words) which does all four of the following:%
+% Identifies the purpose/s of the source (What change do you think the author
+% hoped would happen when people read this source?)% Explains who you think
+% the intended audience of the source is, and why you think this% Explains some
+% key strengths of the source and how it can be useful as you investigate your
+% topic% Explains possible limitations or weaknesses you see in the source%
+% (e.g., credibility, scope of information, author bias, etc.) Keep in mind%
+% that you might have to do a little additional research to get some other%
+% perspectives on your source to evaluate its reliability (e.g., book reviews,%
+% author bios, original publication dates, etc.)
 
@@
 
-Citation: \cite{stokes2021}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/15r5l0d/alma991025892758804876
+Citation: \cite{stokes2021}:
+\\
+Link : \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/15r5l0d/alma991025892758804876}
+\\
 
-\section{Newspaper}
+The purpose of the book is to educate those looking into copyright law for
+art and the various rules that apply to different types of art, even those
+of non-conventional mediums. As for the intention of the author writing this
+book, I believe he desired to provide a compilation of guidelines regarding
+various areas that copyright touches on regarding art and derivative works. I'm
+rationalizing his purpose as the main consumers of his book are those who work
+in art law, IP law, law students, art house managers, and others in the field,
+who regard his book as a critical source of truth regarding common copyright
+misunderstandings and education. I intend to use this source to understand
+the basics of copyright law and gain some insight on how copyright law has
+applied to derivative works in the past. In essence, I plan to use this source
+to develop the foundation of copyright that my essay will build upon. Some
+weaknesses with this source are that it was published in 2001, almost 24
+years ago, so I doubt that it'll include anything of value regarding AI.
+
+\section{Newspaper Article}
 
 Citation: \cite{thomas2024}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_proquest_newspapers_2937453324
+\\
+Link : \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CD_SCR_INST/ojisf2/cdi_proquest_newspapers_2937453324}
+\\
+
+The purpose of this article is to report the recent developments regarding
+the failure of the UK to create a regulatory body to govern AI training
+and usage of copyrighted material. This source is useful for my research
+because it goes into detail about the struggles present regulatory bodies
+have regarding the establishment of an AI regulatory body. The failures are a result
+of lack of understanding / judicial precedent. The audience for
+this article would be the daily readers of "The Financial Times" and those
+interested in the developments of AI regulatory bodies. Some weaknesses with
+this article are that it's fairly short, so it might not go as deep as I
+would like, which might require me to investigate other sources. I definetly want to
+investigate more articles, especially more in the programming space as I'm leaning
+for the core of my paper being focused on Code outputted by AI and the legality behind that.
 
@@
 Citation: \cite{ma2024}
-Link: https://ucsc.primo.exlibrisgroup.com/permalink/01CDL_SCR_INST/ojisf2/cdi_ieee_primary_10440501
+\\
+Link : \url{https://ucsc.primo.exlibrisgroup.com/permalink/01CD_SCR_INST/ojisf2/cdi_ieee_primary_10440501}
+\\
+
+The purpose of this academic paper is to share their academic findings on
+new techniques to identify the source of code, i.e., whether it's from an
+AI or a human, and even possibly the origin of that code. This is extremely
+relevant to my project because the fact that active research is being done
+on tracing the sources of derivative AI works could, in the near future,
+make for a comprehensive case on the distinction between fair use and
+plagiarism. I'm quite excited to read the paper, but one downside I can
+think of is that it's fairly new, so it might not be fully peer-reviewed,
+but it should be interesting nonetheless. The paper also talks about some
+open source tools they created that can identify the origins of some
+code and will tell you if it comes from any of the code repositories online
+that they have indexed. Im quite excited to give this a try, I might even be
+able to show some results in my paper!
 
@@
 Citation: \cite{bloomberglaw2023}
-Link: https://www.youtube.com/watch?v=bRqwTP2eKJY
+\\
+Link : \url{https://www.youtube.com/watch?v=bRqwTP2eKJY}
+\\
+
+The purpose of this video is to inform the general public about recent
+developments in artificial intelligence and the capability for copyright
+law to stop them, as it currently stands. This source is going to be useful
+because its focus is purely on information regarding the topic at hand and
+comes from a reliable source, Bloomberg Law. The audience for this would
+be the general public on YouTube who happen to have this video recommended,
+and maybe some astute followers of Bloomberg Law. Some downsides to this are
+that it is a relatively short video, so I'm a bit concerned about its depth,
+but other than that, it's a credible source with a lot of relevance. I'm
+probably going to end up looking for some more videos that
+go deeper into depth in certain areas, like any existing cases regarding AI and copyright,
+and how those went.
 

### 2025-02-15 paper/main.tex
800 words!

@@
 
-\IEEEPARstart{W}{rite} why is important to do this experiment, what background is needed, what technology has been used in this session, you can also talk briefly about what other technology exist but was not used here.
-Then explain briefly how the experiment was conducted, what measurements were taken, what technology is used (acquisition system, sensors, software), if calculations were done, what calculations were done, what decisions were made, and what the final result was (explained in a concise way with words).
-Writing “good” reports requires much thought, organization and editing but the rewards are
-great. Those students who can master good technical writing skills will find greater success and
-opportunity as professionals in industry.
+\IEEEPARstart{T}{he} emergence of AI tools has, no doubt, changed many aspects of
+how work is approached in many professions, but the greatest impact has been on
+software engineering. New tools like Github Copilot, an AI assisted code generation
+tool thats usable in many modern code editors today, boasts a 2x speedup of feature
+completions and a large boost in productivity for its users \cite{github}. However
+accurate those claims may be, theres no doubt that these tools are being used
+widely by the developer population, and they arent going away any time soon.
 
-% \\
-%thesis
+However the code generated by these tools must come from somewhere. Many models
+source their training data from the public internet, but not everything in public access
+allows for commercial / derivative use. Such models ignore this step,
+jumping straight towards using this data with any disregard for copyright protections in place.
+While copyright has been slow in the past, there is no doubt the legal systems around the world
+will regulate and form precedent for these utilites; Inevitably placing their users
+under risk.
+% WARN: not sure this is the cleanest way to segue into my theses
+
+\textbf {
   For those concerned with the legality of the software they produce, the usage of
@@
 they will become succeptible to copyright law in the near future.
+}
 
@@
 
-% - Go down into the history of copyright, what its
-% definition is, and how it has been interpreted in the past. Really tie
-% it in for the reader so it's fully clear how my argument builds upon
-% this foundational information.
-%   - The book by Stokes should have a lot of relevant information that
-%     I can summarize and cite in this section.
+To help understand the context that this paper resides in, below are
+lay-person explanations of AI training, Software Licensure, AI tools, and
+more.
+
+\subsection{Data Acquisition}
+
+The way AI development labs gather data for their models is
+mainly through web scrapers. Web scrapers are programs that access a
+immense number of websites, downloading and orgranizing
+the all the data they find \cite{Miquido}. The gathered data
+is then used to train whichever model they are interested in.
+
+The modern way for a website to prevent a webscraper from
+downloading its contents is a file called a `robots.txt`,
+that any honest web scraper would look for first, and obey
+the rules inside \cite{robots}. The problem with this "trust me" approach
+is that a dishonest, or even badly programmed, web scraper
+can come along and look past this file and do whatever they please\cite{robots}.
+
+% TODO: could talk about how copilot has access to github, largest source code repo
+
+\subsection{Software Licenses}
 
@@
 
+While it may come as a suprise to the average person,
+even code nowadays has some kind of protection against
+copying / un-permitted usage. The mechanism for this
+is called a "Software License"\cite{Blackduck}.
+The code that these licenses protect is called "source code".
+There exist many kinds of licenses, mainly meant for
+open use towards the public, but there are a two that are crucial to understand.
+
+\begin{IEEEitemize}
+\item Copy Left 
+\\
+  A "Copy Left" license allows the general public to view and do whatever they
+  would like with the source code, but they enforce that any derivative must
+  also use the same license. In effect this is a strictly anti-commercial license
+  as its quite hard for a buisness to use Copy Left Licensed software as
+  anything they produce using that code must have the same
+  Copy Left license, and as a result live in the public domain.
+  \cite{Blackduck}
+
+\item Proprietary 
+\\
+A "Proprietary" license are the most restrictive, as they prevent any viewer / user from
+copying, modifying, redistrbuting, etc \cite{Blackduck}. They are the defaco type of license for any
+commercial code, as they protect code the best, and are legally viable \cite{harvard}.
+
+\end{IEEEitemize}
+
+\subsection{AI-Powered Tools}
+
+The most popular AI tool for developers is Github Copilot, which
+helps developers as they write code. Its most important capability, in
+the context of this work, is its power to automatically generate code when
+you ask. The same capability exists for Claude, OpenAI's models, and others,
+where they have the capacity to take a description of what the
+user wants, and can write code to perform that task \cite{s_2023}. For example, If we
+want to make our own snake game, we could trivially ask a model to
+program the snake game.
+
+\subsection{Copyright}
+
+% - Go down into the history of copyright, what its
+% definition is, and how it has been interpreted in the past. Really tie
+% it in for the reader so it's fully clear how my argument builds upon
+% this foundational information.
+%   - The book by Stokes should have a lot of relevant information that
+%     I can summarize and cite in this section.
+
 % - Usage of AI tools in software engineering. Background information about
@@
 %     1st paragraph, academic paper)
+
+% \\
+%thesis
 
@@
 
-\appendices
-\section{Hand calculations (or name your title for appendix subtitle)}
-List any extra evidence such as photos of the session, that may help you support your claims.
-You can include all hand calculations, extra graphs and plots, simulation results, etc.
-
 % use section* for acknowledgment
@@
 
-% Examples of references:  \\[0.001in]
-
-% Example of data book:\\[0.1in]
-% [2] National Operational Amplifiers Databook. Santa Clara: National Semiconductor
-% Corporation, 1995 Edition, p. I-54. \\[0.1in]
-% Example of textbook: \\[0.1in]
-% [3]M. Young, The Technical Writer’s Handbook. Mill Valley, CA: University Science, 1989.\\[0.1in]
-% Example of scientific journal paper:\\[0.1in]
-% [4] J.W. Smith, L.S. Alans and D.K. Jones, “An operational amplifier approach to
-% active cable modeling”, IEEE Transactions on Modeling, vol. 4, no. 2, 1996, pp.
-% 128-132.\\[0.1in]
-% Example of conference paper proceedings:\\[0.1in]
-% [5] J.W. Smith, L.S. Alans and D.K. Jones, “Active cable models for lossy
-% transmission line circuits”, in Proc. 1995 IEEE Modeling Symposium, 1996, pp.
-% 1086-89.\\[0.1in]
-
-% Example of Internet web page:\\[0.1in]
-% [6] Approximate material properties in isotropic materials. Milpitas, CA: Specialty
-% Engineering Associates, Inc. web site: www.ultrasonic.com, downloaded Aug. 20,
-% 2001.
-
-% List and number all bibliographical 
-% references at the end of your paper in {\bf 9 or 10 point} Times, with 10-point interline spacing.
-When referenced within the text, enclose the citation number in square brackets, for example [1].
-\\
-% Use IEEE format.
-Cite any external work that you used (data sheets, text books, Wikipedia articles, .
-.
-.
-).
-If you get a formula from a Wikipedia article, you must cite the article, giving the title, the URL, and the data you accessed the article as a minimum.
-If you copy a figure, not only must you cite the article you copied from, but you must give explicit figure credit in the caption for the figure: This image copied from .
-.
-.
-.
-If you modify a figure or base your figure on one that has been published elsewhere, you still need to give credit in the caption: This image adapted from .
-.
-.
-.\\[0.1in]
-
-% that's all folks
 \end{document}

### 2025-02-18 paper/main.tex
mostly done with paper

@@
   For those concerned with the legality of the software they produce, the usage of
-AI-generated code should be avoided as their trustworthiness is dubious and
-they will become succeptible to copyright law in the near future.
+AI-generated code should be avoided as soon as possible, as they could become succeptible to
+copyright law in the near future.
 }
@@
 
-\subsection{Copyright}
-
-% - Go down into the history of copyright, what its
-% definition is, and how it has been interpreted in the past. Really tie
-% it in for the reader so it's fully clear how my argument builds upon
-% this foundational information.
-%   - The book by Stokes should have a lot of relevant information that
-%     I can summarize and cite in this section.
-
 % - Usage of AI tools in software engineering. Background information about
@@
 
-% \\
+\subsection{Copyright}
+
+Copyright is a mechanism used to protect created works from direct copying
+but not a sufficiently derivative use or one that gives adequate credit to
+the original author \cite[p.~55]{stokes2021}. There has been one landmark
+case regarding copyright and programming, Google INC v. Oracle America, Inc,
+which regards the copying of generic and widely known API code by Google
+from Oracle \cite{harvard}. API in short means that its code that acts as a
+abstracted layer, such that the user doesnt have to think about whats going
+on underneath. Think of it like me making my own laptop, but still keeping
+around the QWERTY keyboard so the users of my laptop dont have to learn a
+whole new keyboard layout. The ruling stated that its alright for google to
+copy this code because they were doing it in the interest of the general
+public and thought it wasnt possible to copyright something so generic,
+leading to google winning the case.
+
+% - Go down into the history of copyright, what its
+% definition is, and how it has been interpreted in the past. Really tie
+% it in for the reader so it's fully clear how my argument builds upon
+% this foundational information.
+%   - The book by Stokes should have a lot of relevant information that
+%     I can summarize and cite in this section.
+
 %thesis
@@
 \section{AI and Code Generation}
+
+AI has been getting better and better at generating
+code \cite{codesignal}, due to the vasty increasing training data
+these models are harvesting from the web \cite{lacour_2024}.
+Especially with many popular code repositories being open online,
+its fairly straightforward to assume that they are being used for training.
+While its impossible to know exactly whats being used as training data and
+what isnt by these large companies, they arent making it any easier with their
+lack of clarity and reassurance \cite{willison_2023}. Therefore, it can be
+reasonably assumed that licensed code that is public purview is also
+being used as training data.
+
+The issue then arises with the licensure of the code ingested by the model.
+Whether its under a "Proprietary" license or a "Copy Left" license, the
+end user could be in trouble.
+
+A Proprietary license would bar any derivative usage, putting the
+user in deep trouble if found out, whether they're trying to publicize
+their code or not.
+
+A Copy Left, while less troublesome, an entity trying to privatize their code
+would fail to uphold the conditions of the license, which demands that any derivative
+works also be in the public domain.
+
+We havent even gotten to the fact that many licenses require attribution to the
+original author, which would be completely lost in this process of ai ingestion
+and generation.
 
@@
 % TODO: maybe change this name?
-\section{Tracking}
+\section{Detecting the Origins of Generated Code}
+
+While it may seem impossible, If there was a way to figure out where
+the code generated by an AI came from, any users of the generated code
+could be in huge trouble depending on the licensure of the source code.
+Such technology doesnt exist today but is tending towards that direction,
+as seen in this study: \cite{ma2024}. They dive deep into the possibility
+of detecting whether or not code generated by a model can be traced
+back / verified to be in some dataset.
+
+Obviously this hasn't been attempted on mainstream models, but
+with their findings being so fruitful, its only a matter of time
+before new research builds off this foundation to see if
+generated code has its roots on public code. Logically then,
+source code authors could audit whether or not others have indirectly used their
+source code, via this AI ingestion and generation proxy. Now a solid case
+can be built up by authors with strict licenses, that this usage is
+in violation of their licenses and the derivate users now face
+legal trouble.
+
+\section{Forward Compliance}
+
+While origin analysis of AI-generated code is not yet developed, preventative
+action must be taken now by those interested in upholding the legality of their
+software. As this technology develops, the risk of legal trouble only increases.
+
+Forward compliance simply means to disassociate with AI-generation tools, and
+return to a "traditional" style of programming. This is doubley-so for corporate
+projects which would face even higher repurcussions by any future lawsuits.
+
+While some may argue that the process of AI-generating code is transformative by
+defenition, but currently there exists no precedent, so claming as such is meaningless.
+When dealing with Copyright, its best to live on the side of pessimism, so
+treating AI-generation as akin to copying allows users of these tools
+to be protected in case future precedent is pessimistic as well.
+
+Others can argue that the copying of code has precedent, and is allowed according
+to Google INC v. Oracle America Inc., but a deeper inspection of the case details must
+be had. The copying of the API code was only allowed because its value lay
+in the familiarity the general public already had with it. Additionally this API code
+lacked any of the deeper functionality which could be copyrighted and protected, its sematics
+ruled to be too abstract \cite{harvard}.
+
+This reasoning cannot be used for all code however,
+as the AI-tools can generate anything from this API-like code, to code that performs
+real work, with no care for the licensure of either. If an author were to form a case
+claiming that their proprietary code was "copied" and now exists with an unauthorized
+holder, using the afforementioned origin anazlyzer to show the means of "copying,
+the results of this case would turn out very different.
 
@@
 
+There exists a real legal threat, maybe not now but certainly in the near future,
+for those using AI-generated code within their produts, doubly-so if its commercial
+in nature. As of right now there is no way to tell if the code generated comes
+from a open-source repository or one thats heavily licensed. With the research
+on origin analyzers only developing, its very reasonable for AI-generated code
+to be back tracked to its source, leading users to fall under jurisdiction of
+this source code. For those concerned with the legality of their code, its
+best to stray away from these tools.
+
 % Summarize my point with an emphasis on my thesis.
@@
 % use section* for acknowledgment
-\section*{Acknowledgment}
-The authors would like to thank...
+\section*{Acknowledgments and Notes}
+I'd like to thank Dr.Kirsch and my peer reviewers for helping this essay come together. 
+One thing I'd like to note are that the text formatter im using for this template does
+not allow for citations to be bolded, so note that any references to \cite{stokes2021},
+\cite{harvard} and \cite{ma2024} are my peer-reviewed sources, sorry for the trouble.
 

### 2025-02-18 paper/main.tex
done with proofread

--- 2025-02-15 paper/main.tex
@@
 
-\IEEEPARstart{T}{he} emergence of AI tools has, no doubt, changed many aspects of
-how work is approached in many professions, but the greatest impact has been on
-software engineering. New tools like Github Copilot, an AI assisted code generation
-tool thats usable in many modern code editors today, boasts a 2x speedup of feature
-completions and a large boost in productivity for its users \cite{github}. However
-accurate those claims may be, theres no doubt that these tools are being used
-widely by the developer population, and they arent going away any time soon.
-
-However the code generated by these tools must come from somewhere. Many models
-source their training data from the public internet, but not everything in public access
-allows for commercial / derivative use. Such models ignore this step,
-jumping straight towards using this data with any disregard for copyright protections in place.
-While copyright has been slow in the past, there is no doubt the legal systems around the world
-will regulate and form precedent for these utilites; Inevitably placing their users
-under risk.
+\IEEEPARstart{T}{he} emergence of AI tools has, no doubt, changed many
+aspects of how work is approached in various professions,
+but the greatest impact has been on software engineering.
+New tools like Github Copilot, an AI-assisted code-generator
+which is usable in many modern code editors today boasts
+a 2x speedup of feature completions and a large boost in
+productivity for its users \cite{github}. However accurate those claims
+maybe, there's no doubt that these tools are being used widely
+by the developer population, and they aren't going away any
+time soon.
+However, the code generated by these tools must come from
+somewhere. Many models source their training data from the
+public internet, but not everything in public access allows for
+commercial/derivative use. Such models ignore this step,
+jumping straight towards using this data without any regard
+for copyright protections in place. While copyright has been
+slow in the past, there is no doubt the legal systems around
+the world will regulate and form precedents for these utilities;
+Inevitably placing their users at risk.
 % WARN: not sure this is the cleanest way to segue into my theses
@@
 
-To help understand the context that this paper resides in, below are
-lay-person explanations of AI training, Software Licensure, AI tools, and
-more.
+% To help understand the context that this paper resides in, below are
+% lay-person explanations of AI training, Software Licensure, AI tools, and
+% more.
+
+To help understand the context this paper resides in,
+below are lay-person explanations of AI tools / training, Software
+Licensure, and more.
 
@@
 the rules inside \cite{robots}. The problem with this "trust me" approach
-is that a dishonest, or even badly programmed, web scraper
+is that a dishonest, or even badly programmed web scraper
 can come along and look past this file and do whatever they please\cite{robots}.
-
-% TODO: could talk about how copilot has access to github, largest source code repo
 
@@
 
-While it may come as a suprise to the average person,
-even code nowadays has some kind of protection against
+While it may come as a surprise to the average person,
+code nowadays has some kind of protection against
 copying / un-permitted usage. The mechanism for this
@@
 The code that these licenses protect is called "source code".
-There exist many kinds of licenses, mainly meant for
-open use towards the public, but there are a two that are crucial to understand.
+There exist many kinds of permits, mainly meant for
+open use by the public, but there are two that are crucial to understand.
 
@@
   would like with the source code, but they enforce that any derivative must
-  also use the same license. In effect this is a strictly anti-commercial license
-  as its quite hard for a buisness to use Copy Left Licensed software as
+  also use the same license. In effect, this is a strictly anti-commercial license
+  as it is quite hard for a business to use Copy Left Licensed software as
   anything they produce using that code must have the same
-  Copy Left license, and as a result live in the public domain.
+  Copy Left license, and as a result, live in the public domain.
   \cite{Blackduck}
@@
 \\
-A "Proprietary" license are the most restrictive, as they prevent any viewer / user from
-copying, modifying, redistrbuting, etc \cite{Blackduck}. They are the defaco type of license for any
+A "Proprietary" license is the most restrictive, as it prevents any viewer/user from
+copying, modifying, redistributing , etc \cite{Blackduck}. They are the defacto type of license for any
 commercial code, as they protect code the best, and are legally viable \cite{harvard}.
@@
 you ask. The same capability exists for Claude, OpenAI's models, and others,
-where they have the capacity to take a description of what the
+where they can take a description of what the
 user wants, and can write code to perform that task \cite{s_2023}. For example, If we
@@
 program the snake game.
-
-\subsection{Copyright}
-
-% - Go down into the history of copyright, what its
-% definition is, and how it has been interpreted in the past. Really tie
-% it in for the reader so it's fully clear how my argument builds upon
-% this foundational information.
-%   - The book by Stokes should have a lot of relevant information that
-%     I can summarize and cite in this section.
 
@@
 
-% \\
+\subsection{Copyright}
+
+% Copyright is a mechanism used to protect created works from direct copying
+% but not a sufficiently derivative use or one that gives adequate credit to
+% the original author \cite[p.~55]{stokes2021}. There has been one landmark
+% case regarding copyright and programming, Google INC v. Oracle America, Inc,
+% which regards the copying of generic and widely known API code by Google
+% from Oracle \cite{harvard}. API in short means that its code that acts as a
+% abstracted layer, such that the user doesnt have to think about whats going
+% on underneath. Think of it like me making my own laptop, but still keeping
+% around the QWERTY keyboard so the users of my laptop dont have to learn a
+% whole new keyboard layout. The ruling stated that its alright for google to
+% copy this code because they were doing it in the interest of the general
+% public and thought it wasnt possible to copyright something so generic,
+% leading to google winning the case.
+
+Copyright is a mechanism used to protect created works from direct copying
+but not a sufficiently derivative use or one that gives adequate credit to
+the original author \cite[p.~55]{stokes2021}. There has been one landmark
+case regarding copyright and programming, Google INC v. Oracle America, Inc.,
+which regards the copying of generic and widely known API code by Google
+from Oracle \cite{harvard}. API in short means that its code acts as an
+abstracted layer, such that the user doesn't have to think about what's going
+on underneath. Think of it like me making a new laptop, but still keeping
+around the QWERTY keyboard so the users of my laptop don't have to learn a
+whole new keyboard layout. The ruling stated that it was all right for Google to
+copy this code because they were doing it in the interest of the general
+public and thought it wasn't possible to copyright something so generic,
+leading to Google winning the case.
+
+% - Go down into the history of copyright, what its
+% definition is, and how it has been interpreted in the past. Really tie
+% it in for the reader so it's fully clear how my argument builds upon
+% this foundational information.
+%   - The book by Stokes should have a lot of relevant information that
+%     I can summarize and cite in this section.
+
 %thesis
@@
 \section{AI and Code Generation}
+
+% AI has been getting better and better at generating
+% code \cite{codesignal}, due to the vasty increasing training data
+% these models are harvesting from the web \cite{lacour_2024}.
+% Especially with many popular code repositories being open online,
+% its fairly straightforward to assume that they are being used for training.
+% While its impossible to know exactly whats being used as training data and
+% what isnt by these large companies, they arent making it any easier with their
+% lack of clarity and reassurance \cite{willison_2023}. Therefore, it can be
+% reasonably assumed that licensed code that is public purview is also
+% being used as training data.
+
+% The issue then arises with the licensure of the code ingested by the model.
+% Whether its under a "Proprietary" license or a "Copy Left" license, the
+% end user could be in trouble.
+
+% A Proprietary license would bar any derivative usage, putting the
+% user in deep trouble if found out, whether they're trying to publicize
+% their code or not.
+
+% A Copy Left, while less troublesome, an entity trying to privatize their code
+% would fail to uphold the conditions of the license, which demands that any derivative
+% works also be in the public domain.
+
+% We havent even gotten to the fact that many licenses require attribution to the
+% original author, which would be completely lost in this process of ai ingestion
+% and generation.
+
+AI has been getting better and better at generating
+code \cite{codesignal}, due to the increasing training data
+the AI companies are harvesting from the web \cite{lacour_2024}.
+Especially with many popular code repositories being open source, meaning anyone
+online can view them, 
+it can be assumed that they are being used for training.
+While it's impossible to know exactly what's being used as training data and
+what isn't by these large companies, they aren't making it any easier with their
+lack of clarity and reassurance \cite{willison_2023}. Therefore, it can be
+reasonably assumed that licensed code that is on the public web is also
+being used as training data.
+
+The issue then arises with the licensure of the code ingested by the model.
+Whether it's under a "Proprietary" license or a "Copy Left" license, the
+end user could be in trouble.
+
+A Proprietary license would bar any derivative usage, putting the
+user in deep trouble if found out, whether they're trying to publicize
+their code or not.
+
+A Copy Left, while less troublesome, would mean that an entity trying to privatize their code
+would fail to uphold the conditions of the license, which demands that any derivative
+works also be in the public domain.
+
+We haven't even gotten to the fact that many licenses require attribution to the
+original author, which would be completely lost in this process of AI ingestion
+and generation.
 
@@
 % TODO: maybe change this name?
-\section{Tracking}
+\section{Detecting the Origins of Generated Code}
+
+% While it may seem impossible, If there was a way to figure out where
+% the code generated by an AI came from, any users of the generated code
+% could be in huge trouble depending on the licensure of the source code.
+% Such technology doesnt exist today but is tending towards that direction,
+% as seen in this study: \cite{ma2024}. They dive deep into the possibility
+% of detecting whether or not code generated by a model can be traced
+% back / verified to be in some dataset.
+
+% Obviously this hasn't been attempted on mainstream models, but
+% with their findings being so fruitful, its only a matter of time
+% before new research builds off this foundation to see if
+% generated code has its roots on public code. Logically then,
+% source code authors could audit whether or not others have indirectly used their
+% source code, via this AI ingestion and generation proxy. Now a solid case
+% can be built up by authors with strict licenses, that this usage is
+% in violation of their licenses and the derivate users now face
+% legal trouble.
+
+While it may seem impossible, If there was a way to figure out where
+the code generated by an AI came from, any users of the generated code
+could be in huge trouble depending on the licensure of the source code.
+Such technology doesn't exist today but is tending toward that direction,
+as seen in this study: \cite{ma2024}. They dive deep into the possibility
+of detecting whether or not code generated by a model can be traced
+back / verified to be in some dataset. They conclude that its
+possible for some opensource models who are trained on specific datasets
+but more is certainly possible \cite{ma2024}.
+
+This hasn't been attempted on mainstream models, but
+with their findings being so fruitful, it's only a matter of time
+before new research builds off this foundation to see if
+generated code has its roots in publicly availible code. Logically then,
+source code authors could audit whether or not others have indirectly used their
+source code, via this AI ingestion and generation proxy. Now a solid case
+can be built up by authors with strict licenses, that this usage is
+in violation of their licenses and the derivate users now face
+legal trouble.
+
+\section{Forward Compliance}
+
+% While origin analysis of AI-generated code is not yet developed, preventative
+% action must be taken now by those interested in upholding the legality of their
+% software. As this technology develops, the risk of legal trouble only increases.
+
+% Forward compliance simply means to disassociate with AI-generation tools, and
+% return to a "traditional" style of programming. This is doubley-so for corporate
+% projects which would face even higher repurcussions by any future lawsuits.
+
+% While some may argue that the process of AI-generating code is transformative by
+% defenition, but currently there exists no precedent, so claming as such is meaningless.
+% When dealing with Copyright, its best to live on the side of pessimism, so
+% treating AI-generation as akin to copying allows users of these tools
+% to be protected in case future precedent is pessimistic as well.
+
+% Others can argue that the copying of code has precedent, and is allowed according
+% to Google INC v. Oracle America Inc., but a deeper inspection of the case details must
+% be had. The copying of the API code was only allowed because its value lay
+% in the familiarity the general public already had with it. Additionally this API code
+% lacked any of the deeper functionality which could be copyrighted and protected, its sematics
+% ruled to be too abstract \cite{harvard}.
+
+% This reasoning cannot be used for all code however,
+% as the AI-tools can generate anything from this API-like code, to code that performs
+% real work, with no care for the licensure of either. If an author were to form a case
+% claiming that their proprietary code was "copied" and now exists with an unauthorized
+% holder, using the afforementioned origin anazlyzer to show the means of "copying,
+% the results of this case would turn out very different.
+
+While the origin analysis of AI-generated code is not yet developed, preventative
+action must be taken now by those interested in upholding the legality of their
+software. As this technology develops, the risk of legal trouble only increases.
+
+Forward compliance would simply require one to disassociate with AI-generation tools and
+return to a "traditional" style of programming. This is doubly-so for corporate
+projects which would face even higher repercussions by any future lawsuits.
+
+While some may argue that the process of AI-generating code is transformative by
+definition, currently there exists no precedent, so claiming as such is meaningless.
+When dealing with Copyright, it's best to live on the side of pessimism, so
+treating AI generation as akin to copying allows users of these tools
+to be protected in case future precedent is pessimistic as well.
+
+Others can argue that the copying of code has precedent, and is allowed according
+to Google INC v. Oracle America Inc., but a deeper inspection of the case details must
+be had. The copying of the API code was only allowed because its value lay
+in the familiarity the general public already had with it. Additionally, this API code
+lacked any of the deeper functionality that could be copyrighted and protected, its semantics
+ruled to be too abstract \cite{harvard}.
+
+This reasoning cannot be used for all code, however,
+as the AI tools can generate anything from this API-like code, to code that performs
+real work, with no care for the licensure of either. If an author were to form a case
+claiming that their proprietary code was "copied" and now exists with an unauthorized
+holder, using the aforementioned origin analysis technique to show the means of "copying,
+the results of this case would turn out very different.
 
@@
 
+% There exists a real legal threat, maybe not now but certainly in the near future,
+% for those using AI-generated code within their produts, doubly-so if its commercial
+% in nature. As of right now there is no way to tell if the code generated comes
+% from a open-source repository or one thats heavily licensed. With the research
+% on origin analyzers only developing, its very reasonable for AI-generated code
+% to be back tracked to its source, leading users to fall under jurisdiction of
+% this source code. For those concerned with the legality of their code, its
+% best to stray away from these tools.
+
+There exists a real legal threat, maybe not now but certainly in the near future
+for those using AI-generated code within their products, doubly so if it is commercial
+in nature. As of right now, there is no way to tell if the code generated comes
+from an open-source repository or one that is heavily licensed. With the research
+of origin analyzers only developing, it's very reasonable for AI-generated code
+to be backtracked to its source, leading users to fall under the jurisdiction of
+this source code. For those concerned with the legality of their code, it's
+best to stray away from these tools.
+
 % Summarize my point with an emphasis on my thesis.

### 2025-02-18 paper/main.tex
done with paper

@@
 \begin{abstract}
-TODO: need to do this later
+  The increasing usage of code-generation tools by the developer community
+  has not considered the legal implications of using AI-generated code. With
+  model training data known to be publicly sourced, the chances of
+  generated code being tied to licensed code are large. New research shows that
+  origin analysis can be performed on the generated code to find its author/host
+  repository which could make way for legal proceedings.
+
 \end{abstract}
